Pillar 1 - Sequential Pattern Mining

### 2019-02-11 Pillar 1 - Sequential Pattern Mining.Rmd
re-organize and re-name headers

# Association Rules and Sequence Rules
For a first exploration of arules, we conceptualise our framework like this:
transaction = student
item = course

## Data Prep: Creating Transactions and Sequences
First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts.

### take, fail, low grade
```{r AR data prep 1}
d_transactions <- list()

@@

### take / not take, pass / fail / not take
```{r transactions not taken}
d_transactions$TPF <- expand.grid(

@@

  # Identifying item
  mutate(
    item_G = paste(item, grade_ceil, sep = "_")
    )
```
### Additional General Dataframes for courses
#### Transcript with Preceding courses per student
```{r}
d_cumulative_transcript <-  d_transactions        %>%
  select(sequenceID, item, eventID)  %>%
  arrange(sequenceID, eventID, item) %>%
  group_by(sequenceID, eventID)      %>%
  summarize_all(paste, collapse=" ") %>%
  arrange(sequenceID, eventID)       %>%
  mutate(
    course_all  = paste(unique(d_transactions$item), collapse = " "),
    course_all  = str_split(course_all, pattern = " "),

@@

### Support
```{r}

#
# Probability oh having a grade equal or lower than x
d_support$G <- d_transactions$taken_PF_HL %>%
  group_by(
    item
    ) %>%
  summarise(
    `0`    = mean(Grade <= 0),
    `1`    = mean(Grade <= 1),
    `2`    = mean(Grade <= 2),
    `3`    = mean(Grade <= 3),
    `4`    = mean(Grade <= 4),
    `5`    = mean(Grade <= 5),
    `6`    = mean(Grade <= 6),
    `7`    = mean(Grade <= 7),
    `8`    = mean(Grade <= 8),
    `9`    = mean(Grade <= 9),
    `10`   = mean(Grade <= 10)
    ) %>%
  gather(
    key   = grade_ceil,
    value = support.grade,
    `0` : `10`,
    convert = TRUE
    )

### Transactions for Apriori
```{r making transactions, message = FALSE}

@@

### Sequences for CSPADE
```{r making sequences}

@@

## Mining Rules
### Apriori Algorithm

@@

The function `compute_support()` computes the support of the lhs and rhs of the rules.

```{r compute_support}
compute_metrics <- function(AR, data_support, type_rule){

@@

We encapsulate the functions `my_apriori()`, `clean_AR()` and `compute_support()` into the function `make_AR()`.

```{r make_AR}
make_AR <- function(data, data_support, type_rule){

@@

```{r AR take}
AR <- list()

@@

```{r AR fail}
AR$PF <- transactions$PF %>%

@@

```{r AR low}
AR$HL <- transactions$HL %>%

@@

```{r AR TPF}
AR$TPF <- transactions$TPF %>%

@@

```{r AR grade}
AR$G <- transactions$G %>%

@@

```{r edit_AR}
edit_AR <- function(AR){

@@

We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(
  AR,
  file = "App/AR.RDATA"
  )

@@

### CSPADE Algorithm
##TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail

>>>>

# Creating Transactions and Sequences
For a first exploration of arules, we conceptualise our framework like this:
transaction = student
item = course

First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts. 
## Data Preparation
### Take, fail, low grade
```{r AR data prep 1}
d_transactions <- list()

@@

### Take / not take, pass / fail / not take
```{r transactions not taken}
d_transactions$TPF <- expand.grid(

@@

  # Identifying item
  mutate(
    item_G = paste(item, grade_ceil, sep = "_")
    )
```
## Additional General Dataframes for courses
#### Transcript with Preceding courses per student
```{r}
d_cumulative_transcript <-  d_transactions        %>%
  select(sequenceID, item, eventID)  %>%
  arrange(sequenceID, eventID, item) %>%
  group_by(sequenceID, eventID)      %>%
  summarize_all(paste, collapse=" ") %>%
  arrange(sequenceID, eventID)       %>%
  mutate(
    course_all  = paste(unique(d_transactions$item), collapse = " "),
    course_all  = str_split(course_all, pattern = " "),

@@

## Transactions
```{r making transactions, message = FALSE}

@@

## Sequences
```{r making sequences}

@@

## Support
```{r}

#
# Probability oh having a grade equal or lower than x
d_support$G <- d_transactions$taken_PF_HL %>%
  group_by(
    item
    ) %>%
  summarise(
    `0`    = mean(Grade <= 0),
    `1`    = mean(Grade <= 1),
    `2`    = mean(Grade <= 2),
    `3`    = mean(Grade <= 3),
    `4`    = mean(Grade <= 4),
    `5`    = mean(Grade <= 5),
    `6`    = mean(Grade <= 6),
    `7`    = mean(Grade <= 7),
    `8`    = mean(Grade <= 8),
    `9`    = mean(Grade <= 9),
    `10`   = mean(Grade <= 10)
    ) %>%
  gather(
    key   = grade_ceil,
    value = support.grade,
    `0` : `10`,
    convert = TRUE
    )
```

# Mining Rules
## Association Rule

### Functions

@@

The function `compute_support()` computes the support of the lhs and rhs of the rules.
```{r compute_support}
compute_metrics <- function(AR, data_support, type_rule){

@@

We encapsulate the functions `my_apriori()`, `clean_AR()` and `compute_support()` into the function `make_AR()`.
```{r make_AR}
make_AR <- function(data, data_support, type_rule){

@@

### take -> taken
```{r AR take}
AR <- list()

@@

### fail -> fail
```{r AR fail}
AR$PF <- transactions$PF %>%

@@

### low grade -> low grade
```{r AR low}
AR$HL <- transactions$HL %>%

@@

### not take -> fail
```{r AR TPF}
AR$TPF <- transactions$TPF %>%

@@

### less than x grade -> less than 6
```{r AR grade}
AR$G <- transactions$G %>%

@@

### Editing AR
```{r edit_AR}
edit_AR <- function(AR){

@@

### Save Association Rules
We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(
  AR,
  file = "App/AR.RDATA"
  )

@@

## Sequence Rules
##TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail
